Home Nighttime Cough Monitoring

### 2025-07-28 Lilah Melzer/cough_monitor_analysis.qmd
additional cough monitor figures

@@

>>>>

## 38

Participant 38 did not have a pulmonary exacerbation.

@@

## 2

Participant 2 had a pulmonary exacerbation starting on night 41.

```{r}
#| warning: false
p2 <- full_join(
  agg_counts,
  cfqr_children_6_11 %>% select(sid, Date, respirat) %>%
    rename(`CFQ-R Children Ages 6-11` = respirat),
  by = join_by(sid, Date)
)
p2 <- full_join(
  p2,
  cfqr_parent_6_13 %>% select(sid, Date, respirat) %>%
    rename(`CFQ-R Caregivers 6-13` = respirat),
  by = join_by(sid, Date)
)
p2 <- p2 %>%
  filter(sid == 2) %>%
  pivot_longer(c(Coughs, `CFQ-R Children Ages 6-11`, `CFQ-R Caregivers 6-13`)) %>%
  filter(!is.na(value))
p2$name <- factor(p2$name,
  levels = c("Coughs", "CFQ-R Children Ages 6-11", "CFQ-R Caregivers 6-13")
)
p2_plot <- ggplot(p2, aes(x = Night, y = value)) +
  geom_point() +
  geom_line() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  facet_wrap(~name, nrow = 3, scales = "free")
p2_plot
ggsave(paste0(home_dir, "/Dissemination/Figures/participant_2.png"),
  plot = p2_plot, width = 9, height = 7, units = "in"
)
```

## 3

Participant 3 had a pulmonary exacerbation starting on night 1.

```{r}
#| warning: false
cfqr_children_12_13$sid <- as.numeric(cfqr_children_12_13$sid)
p3 <- full_join(
  agg_counts,
  cfqr_children_12_13 %>% select(sid, Date, respirat) %>%
    rename(`CFQ-R Children Ages 12-13` = respirat),
  by = join_by(sid, Date)
)
p3 <- full_join(
  p3,
  cfqr_parent_6_13 %>% select(sid, Date, respirat) %>%
    rename(`CFQ-R Caregivers 6-13` = respirat),
  by = join_by(sid, Date)
)
p3 <- p3 %>%
  filter(sid == 3) %>%
  pivot_longer(c(Coughs, `CFQ-R Children Ages 12-13`, `CFQ-R Caregivers 6-13`)) %>%
  filter(!is.na(value))
p3$name <- factor(p3$name,
  levels = c("Coughs", "CFQ-R Children Ages 12-13", "CFQ-R Caregivers 6-13")
)
p3_plot <- ggplot(p3, aes(x = Night, y = value)) +
  geom_point() +
  geom_line() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  facet_wrap(~name, nrow = 3, scales = "free")
p3_plot
ggsave(paste0(home_dir, "/Dissemination/Figures/participant_3.png"),
  plot = p3_plot, width = 9, height = 7, units = "in"
)
```
